Deciding Bitvector Termination with Program Synthesis

### 2014-06-26 papers/termination/paper.tex
minor changes to sec 5
modified kalashnikov + other small things

Limitations: 
\begin{itemize}
\item No recursion.
\item Nested loops.
\item Heap.
\end{itemize}

@@

Up until this point, we looked at examples that are not soundly treated by existing techniques as they 
don't fit in the range of programs covered by these techniques.
Next, we look at some programs that are handled by existing termination tools via dedicated analyses. We show that our method 
uniformly handles them, without the need for any special treatment.

@@

\subsection{Termination and Ranking Functions} \label{sec:ranking.functions}
We represent programs as transition systems with state space $X$ and transition relation $T \subseteq X \times X$.

@@

\begin{definition}[Ranking function]
An injective function $R: X \to Y$ is a ranking function if $Y$ is well-founded and 
$R$ is monotonically decreasing with respect to $T$.  That is
to say:
$$\forall x, x' . T(x, x') \Rightarrow R(x) < R(x')$$
\end{definition}

@@

>>>>

{\bf Limitations.}
For ease of exposition, this language ignores features
such as dynamic memory allocation and function calls. 
\begin{itemize}
\item No recursion.
\item Nested loops.
\item Heap.
\end{itemize}

@@

Up until this point, we looked at examples that are not soundly treated by existing techniques as they 
don't fit in the range of programs covered by these techniques.
Next, we look at some programs that are handled by existing termination tools via dedicated analyses. We show that our method 
uniformly handles them, without the need for any special treatment.
% we are able to compute termination arguments in several interesting case

% Our technique gains from generality. A possible explanation for this (perhaps initially sur-
%prising) fact is that, for synthesis, we are interested in the mere existence of a
%% solution, and the loss of
%% many solutions does not necessarily mean the loss of
%% all solutions of the constraint
% bit-level analysis
%These non-terminating programs represent an important class of
%bugs, especially for denial-of-service related vulnerabilities, where
%an attacker can exploit the overflow. Equally important,
% equally important

@@

\subsection{Termination and Ranking Functions} \label{sec:ranking.functions}
We represent programs as transition systems with state space $X$, transition relation $T \subseteq X \times X$, and set of variables $\mathcal{V}$. 
A state of the program is a valuation of the variables from $\mathcal{V}$.

@@

\begin{definition}[Ranking function]
An injective function ${R:X\to Y}$ is a ranking function if $Y$ is well-founded and 
$R$ is monotonically decreasing with respect to $T$.  That is
to say:
$$\forall x, x' . T(x, x') \Rightarrow R(x) < R(x')$$
\end{definition}

@@

\subsection{The Non-Termination Problem}
